% Shared bibliography (natbib-compatible, AAAI author-year format).
% All entries verified real; new entries added for the venue upgrades:
% InceptionTime, TCN, CTR-GCN, HD-GCN, calibration (Guo et al.), domain
% generalization (Gulrajani & Lopez-Paz), inductive bias (Battaglia et al.),
% Hoeffding 1963, Serfling 1974.
\begin{thebibliography}{30}
\providecommand{\natexlab}[1]{#1}

\bibitem[{Alam et~al.(2024)Alam, Sufian, Dutta, Leo, and Hameed}]{alam2024gmdcsa}
Alam, E.; Sufian, A.; Dutta, P.; Leo, M.; and Hameed, I.~A. 2024.
\newblock GMDCSA-24: A dataset for human fall detection in videos.
\newblock \emph{Data in Brief}, 57: 110892.

\bibitem[{Bai, Kolter, and Koltun(2018)}]{bai2018tcn}
Bai, S.; Kolter, J.~Z.; and Koltun, V. 2018.
\newblock An Empirical Evaluation of Generic Convolutional and Recurrent Networks for Sequence Modeling.
\newblock arXiv:1803.01271.

\bibitem[{Battaglia et~al.(2018)Battaglia, Hamrick, Bapst, et~al.}]{battaglia2018relational}
Battaglia, P.~W.; Hamrick, J.~B.; Bapst, V.; et~al. 2018.
\newblock Relational inductive biases, deep learning, and graph networks.
\newblock arXiv:1806.01261.

\bibitem[{Bradbury et~al.(2018)Bradbury, Frostig, Hawkins, Johnson, Leary, Maclaurin, Necula, Paszke, VanderPlas, Wanderman-Milne, and Zhang}]{jax2018}
Bradbury, J.; Frostig, R.; Hawkins, P.; Johnson, M.~J.; Leary, C.; Maclaurin, D.; Necula, G.; Paszke, A.; VanderPlas, J.; Wanderman-Milne, S.; and Zhang, Q. 2018.
\newblock JAX: composable transformations of Python+NumPy programs.
\newblock \url{http://github.com/google/jax}.

\bibitem[{Chen et~al.(2021)Chen, Zhang, Yuan, Li, Deng, and Hu}]{chen2021ctrgcn}
Chen, Y.; Zhang, Z.; Yuan, C.; Li, B.; Deng, Y.; and Hu, W. 2021.
\newblock Channel-wise Topology Refinement Graph Convolution for Skeleton-Based Action Recognition.
\newblock In \emph{Proceedings of the IEEE/CVF International Conference on Computer Vision (ICCV)}, 13359--13368.

\bibitem[{de~Miguel et~al.(2017)de~Miguel, Brunete, Hernando, and Gambao}]{demiguel2017home}
de~Miguel, K.; Brunete, A.; Hernando, M.; and Gambao, E. 2017.
\newblock Home Camera-Based Fall Detection System for the Elderly.
\newblock \emph{Sensors}, 17(12): 2864.

\bibitem[{Dempster, Petitjean, and Webb(2020)}]{dempster2020rocket}
Dempster, A.; Petitjean, F.; and Webb, G.~I. 2020.
\newblock ROCKET: exceptionally fast and accurate time series classification using random convolutional kernels.
\newblock \emph{Data Mining and Knowledge Discovery}, 34: 1454--1495.

\bibitem[{Dempster, Schmidt, and Webb(2021)}]{dempster2021minirocket}
Dempster, A.; Schmidt, D.~F.; and Webb, G.~I. 2021.
\newblock MiniRocket: A Very Fast (Almost) Deterministic Transform for Time Series Classification.
\newblock In \emph{Proceedings of the 27th ACM SIGKDD Conference on Knowledge Discovery and Data Mining}, 248--257.

\bibitem[{Duan et~al.(2022)Duan, Zhao, Chen, Lin, and Dai}]{duan2022posec3d}
Duan, H.; Zhao, Y.; Chen, K.; Lin, D.; and Dai, B. 2022.
\newblock Revisiting Skeleton-based Action Recognition.
\newblock In \emph{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)}, 2969--2978.

\bibitem[{FallVision Dataset(2024)}]{fallvision2024}
FallVision Dataset. 2024.
\newblock FallVision: A Large-Scale Skeleton Fall Detection Benchmark.
\newblock Harvard Dataverse, DOI:10.7910/DVN/75QPKK.

\bibitem[{Gulrajani and Lopez-Paz(2021)}]{gulrajani2021domain}
Gulrajani, I.; and Lopez-Paz, D. 2021.
\newblock In Search of Lost Domain Generalization.
\newblock In \emph{International Conference on Learning Representations (ICLR)}.

\bibitem[{Guo et~al.(2017)Guo, Pleiss, Sun, and Weinberger}]{guo2017calibration}
Guo, C.; Pleiss, G.; Sun, Y.; and Weinberger, K.~Q. 2017.
\newblock On Calibration of Modern Neural Networks.
\newblock In \emph{Proceedings of the 34th International Conference on Machine Learning (ICML)}, 1321--1330.

\bibitem[{Hoeffding(1963)}]{hoeffding1963}
Hoeffding, W. 1963.
\newblock Probability Inequalities for Sums of Bounded Random Variables.
\newblock \emph{Journal of the American Statistical Association}, 58(301): 13--30.

\bibitem[{Igual, Medrano, and Plaza(2013)}]{igual2013challenges}
Igual, R.; Medrano, C.; and Plaza, I. 2013.
\newblock Challenges, issues and trends in fall detection systems.
\newblock \emph{BioMedical Engineering OnLine}, 12(66).

\bibitem[{Ismail~Fawaz et~al.(2020)Ismail~Fawaz, Lucas, Forestier, Pelletier, Schmidt, Weber, Webb, Idoumghar, Muller, and Petitjean}]{fawaz2020inceptiontime}
Ismail~Fawaz, H.; Lucas, B.; Forestier, G.; Pelletier, C.; Schmidt, D.~F.; Weber, J.; Webb, G.~I.; Idoumghar, L.; Muller, P.-A.; and Petitjean, F. 2020.
\newblock InceptionTime: Finding AlexNet for time series classification.
\newblock \emph{Data Mining and Knowledge Discovery}, 34(6): 1936--1962.

\bibitem[{Kwolek and Kepski(2014)}]{kwolek2014urfd}
Kwolek, B.; and Kepski, M. 2014.
\newblock Human fall detection on embedded platform using depth maps and wireless accelerometer.
\newblock \emph{Computer Methods and Programs in Biomedicine}, 117(3): 489--501.

\bibitem[{Lee et~al.(2023)Lee, Lee, Lee, and Lee}]{lee2023hdgcn}
Lee, J.; Lee, M.; Lee, D.; and Lee, S. 2023.
\newblock Hierarchically Decomposed Graph Convolutional Networks for Skeleton-Based Action Recognition.
\newblock In \emph{Proceedings of the IEEE/CVF International Conference on Computer Vision (ICCV)}, 10444--10453.

\bibitem[{Lin and Dong(2021)}]{lin2021robot}
Lin, C.-B.; and Dong, S.-P. 2021.
\newblock Human Fall Detection with a Robot Using Gait Skeleton and Body Pose.
\newblock \emph{Applied Sciences}, 11(20): 9596.

\bibitem[{Liu et~al.(2020)Liu, Zhang, Chen, Wang, and Ouyang}]{liu2020msg3d}
Liu, Z.; Zhang, H.; Chen, Z.; Wang, Z.; and Ouyang, W. 2020.
\newblock Disentangling and Unifying Graph Convolutions for Skeleton-Based Action Recognition.
\newblock In \emph{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)}, 143--152.

\bibitem[{Middlehurst et~al.(2024)Middlehurst, Ismail-Fawaz, Guillaume, Holder, Guijo-Rubio, Bulatova, Tsaprounis, Mentel, Walter, Sch{\"a}fer, and Bagnall}]{middlehurst2024aeon}
Middlehurst, M.; Ismail-Fawaz, A.; Guillaume, A.; Holder, C.; Guijo-Rubio, D.; Bulatova, G.; Tsaprounis, L.; Mentel, L.; Walter, M.; Sch{\"a}fer, P.; and Bagnall, A. 2024.
\newblock aeon: a Python toolkit for learning from time series.
\newblock \emph{Journal of Machine Learning Research}, 25(124): 1--10.

\bibitem[{Mubashir, Shao, and Seed(2013)}]{mubashir2013survey}
Mubashir, M.; Shao, L.; and Seed, L. 2013.
\newblock A survey on fall detection: Principles and approaches.
\newblock \emph{Neurocomputing}, 100: 144--152.

\bibitem[{Pang et~al.(2021)Pang, Shen, Cao, and van~den Hengel}]{pang2021anomaly}
Pang, G.; Shen, C.; Cao, L.; and van~den Hengel, A. 2021.
\newblock Deep Learning for Anomaly Detection: A Review.
\newblock \emph{ACM Computing Surveys}, 54(2): 1--38.

\bibitem[{Rajpurkar et~al.(2017)Rajpurkar, Hannun, Haghpanahi, Bourn, and Ng}]{rajpurkar2017cardiologist}
Rajpurkar, P.; Hannun, A.~Y.; Haghpanahi, M.; Bourn, C.; and Ng, A.~Y. 2017.
\newblock Cardiologist-Level Arrhythmia Detection with Convolutional Neural Networks.
\newblock arXiv:1707.01836.

\bibitem[{Serfling(1974)}]{serfling1974}
Serfling, R.~J. 1974.
\newblock Probability Inequalities for the Sum in Sampling without Replacement.
\newblock \emph{The Annals of Statistics}, 2(1): 39--48.

\bibitem[{Shi et~al.(2019)Shi, Zhang, Cheng, and Lu}]{shi2019directed}
Shi, L.; Zhang, Y.; Cheng, J.; and Lu, H. 2019.
\newblock Skeleton-Based Action Recognition With Directed Graph Neural Networks.
\newblock In \emph{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)}, 7912--7921.

\bibitem[{Tan et~al.(2022)Tan, Dempster, Bergmeir, and Webb}]{tan2022multirocket}
Tan, C.~W.; Dempster, A.; Bergmeir, C.; and Webb, G.~I. 2022.
\newblock MultiRocket: multiple pooling operators and transformations for fast and effective time series classification.
\newblock \emph{Data Mining and Knowledge Discovery}, 36(5): 1623--1646.

\bibitem[{Yan, Xiong, and Lin(2018)}]{yan2018stgcn}
Yan, S.; Xiong, Y.; and Lin, D. 2018.
\newblock Spatial Temporal Graph Convolutional Networks for Skeleton-Based Action Recognition.
\newblock In \emph{Proceedings of the AAAI Conference on Artificial Intelligence}.

\bibitem[{Zhu et~al.(2025)}]{zhu2025fall}
Zhu, X.; et~al. 2025.
\newblock Fall Detection Using Graph Convolutional Network with Skeleton Sequences.
\newblock \emph{IEEE Sensors Journal}.

\end{thebibliography}
